---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# octaver

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/octaver)](https://CRAN.R-project.org/package=octaver)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/kvasilopoulos/octaver/workflows/R-CMD-check/badge.svg)](https://github.com/kvasilopoulos/octaver/actions)
[![Codecov test coverage](https://codecov.io/gh/kvasilopoulos/octaver/branch/master/graph/badge.svg)](https://codecov.io/gh/kvasilopoulos/octaver?branch=master)
<!-- badges: end -->

The goal of octaver is to provide an interface to Octave 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/octaver")
```
## Session

```{r session}
library(octaver)
find_octave()

## basic example code
pr <- OctaveSession$new()
pr$eval("2+2")

pr$eval("A = 2+2")
pr$eval("A")

pr$kill()
```

## REPL

```{r repl, eval=FALSE, include=FALSE}
OctaveREPL$new()
```

## Knitr engine

```{octave eval = TRUE} 
A = 1;
A
```


## API


### Various .m scripts

m_

### Run

oct_run():
oct_addpath():

### Session & Repl
<!-- > Steam connections -->

oct_session():
oct_repl():

### Knitr

set_oct_engine():

### Read & Write

write_mat():
read_mat():

### Installation helpers

install_oct():
install_pkg():

### Other helpers

has_octave():
octave_path():
find_octave():
list_pkgs():






